Supplementary Information

### 2018-08-09 manuscript/latitudepaper.tex

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=\st{0.637}0.691, $p$\textless0.001; $\beta_0$=\st{0.553}0.663,
  $p$\textless0.001; and $\beta_0$=\st{0.637}0.698, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.212 for link density;
  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.320 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.207 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.037;
  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.007; and
  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.003, $p$=0.036, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=\st{0.007, $p$=0.001}0.005, $p$=0.008) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).

>>>>

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=\st{0.637}0.688, $p$\textless0.001; $\beta_0$=\st{0.553}0.658,
  $p$\textless0.001; and $\beta_0$=\st{0.637}0.695, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.210 for link density;
  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.315 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.205 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.031;
  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.005; and
  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.004, $p$=0.030, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=\st{0.007, $p$=0.001}0.005, $p$=0.008) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).

### 2018-08-09 manuscript/supplement.tex

  \clearpage
  \begin{center}
    \begin{table}[h!]
      \caption{Networks with corrections. Names are as in Table S1. All corrected webs were taken from~\cite{GlobalWeb}. Some links were coded as negative values, decimal values, or values other than 1 that were intended to convey additional information. All were re-coded as 1. In a few cases, entries of -1 indicated links that should not be included in the network (e.g., where primary producers would be interpreted as predators). These entries were changed to 0. Some webs contained missing column or row labels; these were inferred based on species ordering in the complete dimension. Some row or column labels contained sample sizes or life stage information missing from the other dimension, or contained typos in either row or column labels. These were removed such that row and column labels matched. In most webs, predators were given across columns and prey down rows. Where this was not the case, rows and columns were flipped.}
      \label{S2}
      {\footnotesize
      \begin{tabular}{l | p{13cm}}
      Web ID & Type of correction \\
      \hline
      18 & Corrected -1 entry to 1 \\
      22 &  Corrected -1 entries to 1, -2 entries to 0 \\
      23 & Corrected -1 entries to 1 \\
      24 &  Corrected -1 entries to 1 \\
      26 & Corrected decimal entries to 1, -1 entries to 1 \\
      33 & Corrected decimal entries to 1 \\
      37 & Corrected -1 entries to 1 \\
      38 & Converting -1 entries to 1 \\
      39 & Corrected species names \\
      41 & Corrected species names \\
      60 & Corrected species names \\
      80 & Corrected species names \\
      114 & Corrected -1 entry to 1 \\
      117 & Corrected -1 entry to 1 \\
      119 & Corrected -1 entries to 1 \\
      120 & Corrected -1 entries to 1 \\
      153 & Corrected -1 entries to 1 \\
      154 & Corrected -1 entries to 1  \\
      180 &  Corrected entries indicating a primary producer as predator to 0 \\
      181 &  Corrected -1 entries to 1 \\
      182 &  Corrected -1 entries to 1 \\
      183 &  Corrected -1 entries to 1 \\
      202 &  Corrected -1 entries to 1  \\
      213 &  Corrected -1 entries to 1  \\
      214 &  Corrected species names \\
      215 &  Corrected species names \\
      216 &  Corrected species names \\
      217 &  Corrected species names \\
      218 &  Corrected species names \\
      219 &  Corrected species names \\
      220 &  Corrected species names \\
      221 &  Corrected species names \\
      222 &  Corrected species names \\
      223 &  Corrected species names \\
      224 &  Corrected species names \\
      225 &  Corrected species names \\
      \hline
      \end{tabular} }
      \end{table}

>>>>

  \clearpage
  \begin{center}
    \begin{table}[h!]
      \caption{Networks with corrections. Names are as in Table S1. All corrected webs were taken from~\cite{GlobalWeb}. Some links were coded as negative values, decimal values, or values other than 1 that were intended to convey additional information. All were re-coded as 1. In a few cases, entries of -1 indicated links that should not be included in the network (e.g., where primary producers would be interpreted as predators). These entries were changed to 0. Some webs contained missing column or row labels; these were inferred based on species ordering in the complete dimension. Some row or column labels contained sample sizes or life stage information missing from the other dimension, or contained typos in either row or column labels. These were removed such that row and column labels matched. In most webs, predators were given across columns and prey down rows. Where this was not the case, rows and columns were flipped.}
      \label{S2}
      {\footnotesize
      \begin{tabular}{l | p{13cm}}
      Web ID & Type of correction \\
      \hline
      #18 & Corrected -1 entry to 1 \\
      #22 &  Corrected -1 entries to 1, -2 entries to 0 \\
      #23 & Corrected -1 entries to 1 \\
      #24 &  Corrected -1 entries to 1 \\
      #26 & Corrected decimal entries to 1, -1 entries to 1 \\
      33 & Corrected decimal entries to 1 \\
      37 & Corrected -1 entries to 1 \\
      38 & Converting -1 entries to 1 \\
      39 & Corrected species names \\
      41 & Corrected species names \\
      #60 & Corrected species names \\
      80 & Corrected species names \\
      114 & Corrected -1 entry to 1 \\
      117 & Corrected -1 entry to 1 \\
      119 & Corrected -1 entries to 1 \\
      120 & Corrected -1 entries to 1 \\
      #153 & Corrected -1 entries to 1 \\
      #154 & Corrected -1 entries to 1  \\
      #180 &  Corrected entries indicating a primary producer as predator to 0 \\
      #181 &  Corrected -1 entries to 1 \\
      #182 &  Corrected -1 entries to 1 \\
      #183 &  Corrected -1 entries to 1 \\
      202 &  Corrected -1 entries to 1  \\
      213 &  Corrected -1 entries to 1  \\
      214 &  Corrected species names \\
      215 &  Corrected species names \\
      216 &  Corrected species names \\
      217 &  Corrected species names \\
      218 &  Corrected species names \\
      219 &  Corrected species names \\
      220 &  Corrected species names \\
      221 &  Corrected species names \\
      222 &  Corrected species names \\
      223 &  Corrected species names \\
      224 &  Corrected species names \\
      225 &  Corrected species names \\
      \hline
      \end{tabular} }
      \end{table}
